Donor Responses to Civil Society Repression

### 2024-11-05 index.qmd
Add some links and tweaks

---
title: "Donor Responses to Civil Society Repression"
subtitle: "Chapter for the *Handbook of Political Control*"
date: 2024-11-04
author:
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
  attributes:
    corresponding: true
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu
bibliography: references.bib
csl: csl/chicago-author-date.csl
params:
  wordcount: |
    <strong>{{< words-sum body-ref >}} total words</strong>: {{< words-body >}} in the body • {{< words-ref >}} in the references
---

>>>>

---
title: "Donor Responses to Civil Society Repression"
subtitle: "Chapter for the *Handbook of Political Control*"
date: 2024-11-04
author:
- name: Andrew Heiss
  affiliations: 
    - id: gsu
      name: Georgia State University
      department: Andrew Young School of Policy Studies, Department of Public Management and Policy
      address: "55 Park Place NE, #464"
      city: Atlanta
      region: GA
      country: USA
      postal-code: 30303
  orcid: 0000-0002-3948-3914
  url: https://www.andrewheiss.com
  email: aheiss@gsu.edu
  attributes:
    corresponding: true
- name: Suparna Chaudhry
  affiliation: Lewis and Clark College
  orcid: 0000-0003-3506-7590
  url: https://www.suparnachaudhry.com/
  email: schaudhry@lclark.edu

bibliography: references.bib
csl: csl/chicago-author-date.csl

doi: 10.31235/osf.io/9gmhp
doi-title: SocArXiv preprint

params:
  wordcount: |
    <strong>{{< words-sum body-ref >}} total words</strong>: {{< words-body >}} in the body • {{< words-ref >}} in the references
---
